Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-09-03 Scripts/Initial_Analysis.Rmd
Including 1 sd treshold step in proportion analysis

```{r fun_SummaryProp, eval = F, echo =F}

@@

  # Reads taxon data
  proportion_data <- fread(paste(my_path("R",extra_path = "Proportion_2005/"),"proportion_",taxon_key,".csv", sep=""))

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean, na.rm = T) # average spp change from all countries sharing
      ) %>% 
      filter(!is.na(mean_spp))

  }else{
    # summarizes by country
    country_summary <- proportion_data %>% 
      group_by(taxon_key,eez_name,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean,na.rm=T) # average spp change from all countries sharing
      ) %>% 
      filter(!is.na(mean_spp))
    }

@@

The next step is to summarize all species per eez so our results shows average change of all species within an EEZ towards a neighbour

@@

```{r fun_PropChange, eval = F, echo =F}

>>>>

```{r fun_SummaryProp, eval = F, echo =F}
taxon_key <- 600006

@@

  # Reads taxon data
  proportion_data <- fread(paste(my_path("R",extra_path = "Proportion_2005/"),"proportion_",taxon_key,".csv", sep="")) %>% 
    filter(!is.na(eez_neighbour))

  # Identify SSR treshold for natural spatial variability of the stock
  proportion_tresh <- proportion_data %>% 
    filter(time_step == "historical") %>% 
    mutate(
      top_tresh = ensemble_mean+ensemble_sd,
      low_tresh = ensemble_mean-ensemble_sd
    ) %>% 
    select(taxon_key:eez_neighbour,top_tresh:low_tresh) %>% 
    left_join(proportion_data) %>% 
    # Only keeps change if surpasses treshold
    mutate(
      over_tresh = ifelse(ensemble_mean > top_tresh | ensemble_mean < low_tresh,"keep",
                          ifelse(time_step == "historical","keep","drop")
      )
    ) %>% 
    filter(over_tresh == "keep") %>% 
    select(-top_tresh,-low_tresh)

  if(links == "y"){
    # summarizes by country and neighbour
    country_summary <- proportion_tresh %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean, na.rm = T) # average spp change from all countries sharing
      ) %>% 
      filter(!is.na(mean_spp))

  }else{
    # summarizes by country
    country_summary <- proportion_tresh %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% 
      summarise(
        mean_spp = mean(ensemble_mean,na.rm=T) # average spp change from all countries sharing
      ) %>% 
      filter(!is.na(mean_spp))
    }

@@

The next step is to summarize all species per eez so our results shows average change of all species within an EEZ towards a neighbour.

**Note: Contains step to filter out changes less than +-1 s.d.**

@@

```{r fun_PropChange, eval = F, echo =F}
taxon_list <- unique(Transboundary_spp$taxon_key)[1:15]
